---
title: "CESISTA, KJ-FA8"
author: "Kristen Jelaena Cesista"
date: "2025-05-01"
output: pdf_document
---

1. An analogue signal received at a detector, measured in microvolts, is 
normally distributed with mean of 200 and variance of 256.

(a) What is the probability that the signal will exceed 224 microvolts?

(b) What is the probability that it will be between 186 and 224 microvolts?

(c) What is the micro voltage below which 25% of the signals will be?

(d) What is the probability that the signal will be less than 240 microvolts, 
given that it is larger than 210 microvolts?

(e) Estimate the interquartile range.

(f) What is the probability that the signal will be less than 220 microvolts, 
given that it is larger than 210 microvolts?

(g) If we know that a received signal is greater that 200 microvolts, what is 
the probability that is in fact greater than 220 microvolts?

```{r}
signal_mean <- 200
signal_var <- 256
signal_sdev <- sqrt(signal_var)

prob_exceeds_224 <- 1-pnorm(224, signal_mean, signal_sdev)
cat(sprintf("The probability that the signal will exceed 224 micro Voltage is %.4f", 
            prob_exceeds_224))

prob_between_186_224 <- pnorm(224, signal_mean, signal_sdev) - 
  pnorm(186, signal_mean, signal_sdev)
cat(sprintf("\nThe probability that it will be between 186 and 224 micro Voltage
            is %.4f", prob_between_186_224))

quartile_below_25 <- qnorm(0.25, signal_mean, signal_sdev)
cat(sprintf("\nThe micro voltage below which 25 percent of the signals will be %.4f", 
            quartile_below_25))

prob_less_than_240_union_greater_than_210 <- pnorm(240, signal_mean, signal_sdev)- 
  pnorm(210, signal_mean, signal_sdev)
prob_larger_than_210 <- 1 - pnorm(210, signal_mean, signal_sdev)
prob_less_than_240_given_greater_than_210 <- prob_less_than_240_union_greater_than_210 / 
  prob_larger_than_210
cat(sprintf("\nThe probability that the signal will be less than 240 micro Voltage, 
            given that it is larger than 210 micro Voltage is %.4f", 
            prob_less_than_240_given_greater_than_210))

iqr_signal <- qnorm(0.75, signal_mean, signal_sdev) - 
  qnorm(0.25, signal_mean, signal_sdev)
cat(sprintf("\nThe interquartile range is %.4f", iqr_signal))

prob_greater_than_210_union_less_than_220 <- pnorm(220, signal_mean, signal_sdev) - 
  pnorm(210, signal_mean, signal_sdev)
prob_greater_than_210 <- pnorm(210, signal_mean, signal_sdev)
prob_greater_than_210_given_less_than_220 <- prob_greater_than_210_union_less_than_220 / 
  prob_greater_than_210
cat(sprintf("\nThe probability that the signal will be less than 220 micro Voltage, 
            given that it is larger than 210 micro Voltage is %.4f", 
            prob_greater_than_210_given_less_than_220))

prob_greater_than_220 <- 1 - pnorm(220, signal_mean, signal_sdev)
prob_greater_than_200 <- 1- pnorm(200, signal_mean, signal_sdev)
prob_greater_than_220_given_greater_than_200 <- prob_greater_than_220 / 
  prob_greater_than_200
cat(sprintf("\nThe probability that the signal will be greater than 220 
            micro Voltage is %.4f", 
            prob_greater_than_220_given_greater_than_200))
```


2. A manufacturer of a particular type of computer system is interested in 
improving its customer support services. As a first step, its marketing 
department has been charged with the responsibility of summarizing the extent of 
customer problems in terms of system failures. Over a period of six months, 
customers were surveyed and the amount of downtime (in minutes) due to system 
failures they had experienced during the previous month was collected. The average 
downtime was found to be 25 minutes and a variance of 144. If it can be assumed 
that downtime is normally distributed:

(a) obtain bounds which will include 95% of the downtime of all the customers;

(b) obtain the bound above which 10% of the downtime is included.

```{r}
downtime_mean <- 25
downtime_var <- 144
downtime_sdev <- sqrt(downtime_var)

downtime_95_bounds <- bounds_95 <- qnorm(c(0.025, 0.975), downtime_mean, 
                                         downtime_sdev)
cat(sprintf("The bounds which will include 95%% of the downtime of all the 
            costumers are %.3f to %.3f", downtime_95_bounds[1], downtime_95_bounds[2]))

downtime_bound_above_10 <- qnorm (0.9, downtime_mean, downtime_sdev)
cat(sprintf("\nThe bound above which 10%% of downtime included is %.3f", 
            downtime_bound_above_10))
```
