---
title: "SEC 1-FA6 GROUP 10-CESISTA, KJ-FA6"
author: "Kristen Jelaena Cesista"
date: "2025-03-10"
output: pdf_document
---

I. Geometric Distribution. Provide an R code for the geometric distribution. The geometric distribution is a probability distribution that models the number of trials required to achieve the first success in a sequence of Bernoulli trials, where each trial has a constant probability of success.

1. Set the probability of success:  p <- 0.2

2. Generate 1000 random variables from the geometric distribution.

3. Calculate some basic statistics:

mean_x <- mean(x)

var_x <- var(x)

sd_x <- sd(x)

4. Print the results in item 3 with the following output (string): 

Number of trials required to achieve first success:

Mean (in 2 decimal places):

Variance (in 2 decimal places):

Sandard deviation ( in 2 decimal places):

5. Plot the histogram of the results.
```{r}
library(ggplot2)

p <- 0.2
n <- 1000

x <- rgeom(n, prob = p)

mean_x <- mean(x)
var_x <- var(x)
sd_x <- sd(x)

cat("Number of trials required to acheive first success:\n")
cat(sprintf("Mean: %.2f\n", mean_x))
cat(sprintf("Variance: %.2f\n", var_x))
cat(sprintf("Standard deviation: %.2f\n", sd_x))

df <- data.frame(samples = x)

ggplot(data = df, aes(x = samples)) +
  geom_histogram(binwidth = 1, fill = "lightblue", color = "black") +
  labs(title = "Histogram of Random Samples from Geometric Distribution (p = 0.2)",
       x = "Number of Trials",
       y = "Frequency") +
  theme_minimal()

```

II. Hypergeometric Distribution.  Consider a plant manufacturing IC chips of which 10% are expected to be defective. The chips are packed in boxes for export. Before transportation, a sample is drawn from each box. Estimate the probability that the sample contains more than 10% defectives, when:

1. A sample of 10 is selected from a box of 40;
2. A sample of 10 is selected from a box of 5000.

```{r}
m1 = 40 * 0.1
n1 = 40 - m1
m2 = 5000 * 0.1
n2 = 5000 - m2
k = 10

prob_1 <- sum(dhyper(x = c(2:10), m1, n1, k))
prob_2 <- sum(dhyper(x = (2:10), m2, n2, k))

cat("The probability that the sample cotains more than 10% defectives is:\n")
cat(sprintf("%f when a sample of 10 is selected from a box of 40.\n", prob_1))
cat(sprintf("%f when a sample of 10 is selected from a box of 5000.\n", prob_2))

```



