---
title: "SA1"
author: "Kristen Jelaena Cesista"
date: "2025-03-16"
output: pdf_document
---

Problem 1:
A company has three factories producing a product. Factory 1 produces x1 of the 
product, factory 2 produces x2, and factory 3 produces x3, where sum from i = 1 
to 3 of xi = 1. The defective rates of the products are y1, y2, and y3 
respectively, where sum from i = 1 to 3 of yi = 0.12.

Write a program (user input for xi and yi) to calculate the probability that 
a randomly selected product is defective.

Note that your program should render prompt messages to satisfy the following conditions:
0.10 ≤ xi ≤ 0.40 or 10% ≤ xi ≤ 40% and sum from i = 1 to 3 of xi = 1.
0.01 ≤ yi ≤ 0.05 or 1% ≤ yi ≤ 5% and sum from i = 1 to 3 of yi = 0.12.

```{r}
repeat {
    cat("\nEnter values for x1, x2, and x3 (must sum to 1, with each value from 
        0.10 to 0.40):\n")

    x1 <- as.numeric(readline("Enter value of x1: "))
    x2 <- as.numeric(readline("Enter value of x2: "))
    x3 <- as.numeric(readline("Enter value of x3: "))

    if (x1 + x2 + x3 == 1 && 
        x1 >= 0.1 && x1 <= 0.4 && 
        x2 >= 0.1 && x2 <= 0.4 && 
        x3 >= 0.1 && x3 <= 0.4) {
        cat(sprintf("x1 is %f. x2 is %f. x3 is %f\n", x1, x2, x3))
        break
    }

    cat("\nInvalid input. Please follow the constraints:\n")
    cat("- The sum of x1, x2, and x3 must be exactly 1.\n")
    cat("- Each value must be from 0.10 to 0.40.\n")
}

repeat {
    cat("\nEnter values for y1, y2, and y3 (must sum to 0.12, with each value 
        from 0.01 to 0.05):\n")
    
    y1 <- as.numeric(readline("Enter value of y1: "))
    y2 <- as.numeric(readline("Enter value of y2: "))
    y3 <- as.numeric(readline("Enter value of y3: "))

    if (y1 + y2 + y3 == 0.12 && 
        y1 >= 0.01 && y1 <= 0.05 && 
        y2 >= 0.01 && y2 <= 0.05 && 
        y3 >= 0.01 && y3 <= 0.05) {
        cat(sprintf("y1 is %f. y2 is %f. y3 is %f", y1, y2, y3))
        break 
    }

    cat("\nInvalid input. Please follow the constraints:\n")
    cat("- The sum of y1, y2, and y3 must be exactly 0.12.\n")
    cat("- Each value must be from 0.01 to 0.05.\n")
}

prob_defective <- (x1 * y1) + (x2 * y2) + (x3 * y3)
cat(sprintf("The probability that a randomly selected product is defective is 
            %f", prob_defective))
```
Problem 2:
Develop an R program with a front-end interface that allows the user to:

Input the values of a univariate discrete random variable and the associated 
probabilities to obtain the mean and variance. Input the values of a bivariate 
discrete random variable and the associated probabilities to obtain the marginal 
and conditional distributions.

Program Requirements:
The program should compute the mean and variance of each distribution.
It should validate that the probabilities are within the range of 0 to 1 and 
that their total sum is equal to 1.
The program should provide a probability density function (PDF) and cumulative 
distribution function (CDF) plot for the distributions.

```{r}

library(ggplot2)
cat("\nEnter values for univariate discrete random variable X and its probabilities:\n")

x_values <- c()
p_values <- c()
total_p <- 0

repeat {
    cat(sprintf("\n[%d]\n", length(x_values) + 1))
    x <- as.numeric(readline("Enter value of X: "))
    p <- as.numeric(readline("Enter probability P(X): "))

    if (p < 0 || p > 1) {
        cat("Invalid probability. Must be between 0 and 1.\n")
        next
    }

    x_values <- c(x_values, x)
    p_values <- c(p_values, p)
    total_p <- sum(p_values)

    more <- as.numeric(readline("Enter another value? (1-Yes, 0-No): "))
    if (more == 0) break
}

if (total_p != 1) stop("Probabilities must sum to 1.")

mean_x <- sum(x_values * p_values)
var_x <- sum((x_values - mean_x)^2 * p_values)

cat(sprintf("\nMean: %f\nVariance: %f\n", mean_x, var_x))

barplot(p_values, names.arg = x_values, main="Probability Mass Function (PMF)", 
        col="lightblue", xlab="X", ylab="P(X)")
plot(ecdf(x_values), main="Cumulative Distribution Function (CDF)", xlab="X", 
     ylab="F(X)", col="pink")

cat("\nEnter values for bivariate discrete random variable (X, Y) and joint 
    probabilities:\n")

x_values <- c()
y_values <- c()
p_xy <- c()
total_p <- 0

repeat {
    cat(sprintf("\n[%d]\n", length(x_values) + 1))
    x <- as.numeric(readline("Enter value of X: "))
    y <- as.numeric(readline("Enter corresponding value of Y: "))
    p <- as.numeric(readline("Enter joint probability P(X, Y): "))

    if (p < 0 || p > 1) {
        cat("Invalid probability. Must be between 0 and 1.\n")
        next
    }

    x_values <- c(x_values, x)
    y_values <- c(y_values, y)
    p_xy <- c(p_xy, p)
    total_p <- sum(p_xy)

    more <- as.numeric(readline("Enter another pair? (1-Yes, 0-No): "))
    if (more == 0) break
}

if (total_p != 1) stop("Joint probabilities must sum to 1.")

unique_x <- unique(x_values)
unique_y <- unique(y_values)

P_X <- sapply(unique_x, function(x) sum(p_xy[x_values == x]))
P_Y <- sapply(unique_y, function(y) sum(p_xy[y_values == y]))

cat("\nMarginal Distributions:\n")
P_X <- tapply(p_xy, x_values, sum)
P_Y <- tapply(p_xy, y_values, sum)

cat("\nMarginal Distributions:\n")
cat("P(X):\n")
print(P_X)
cat("P(Y):\n")
print(P_Y)

# Compute Mean and Variance
unique_x <- as.numeric(names(P_X))
unique_y <- as.numeric(names(P_Y))

mean_x <- sum(unique_x * P_X)
mean_y <- sum(unique_y * P_Y)

var_x <- sum((unique_x - mean_x)^2 * P_X)
var_y <- sum((unique_y - mean_y)^2 * P_Y)

cat(sprintf("\nMean of X: %f  Variance of X: %f", mean_x, var_x))
cat(sprintf("\nMean of Y: %f  Variance of Y: %f", mean_y, var_y))

# Compute Conditional Distributions
P_X_given_Y <- matrix(0, nrow = length(unique_x), ncol = length(unique_y))
P_Y_given_X <- matrix(0, nrow = length(unique_y), ncol = length(unique_x))

for (i in 1:length(unique_x)) {
  for (j in 1:length(unique_y)) {
    joint_prob <- sum(p_xy[x_values == unique_x[i] & y_values == unique_y[j]])
    
    if (P_Y[j] > 0) {
      P_X_given_Y[i, j] <- joint_prob / P_Y[j]  # P(X | Y)
    }
    
    if (P_X[i] > 0) {
      P_Y_given_X[j, i] <- joint_prob / P_X[i]  # P(Y | X)
    }
  }
}

cat("\nConditional Distributions:\n")
cat("P(X | Y):\n")
print(P_X_given_Y)
cat("P(Y | X):\n")
print(P_Y_given_X)

df <- data.frame(X = x_values, Y = y_values, P = p_xy)
ggplot(df, aes(x = X, y = Y, fill = P)) + 
    geom_tile() + 
    scale_fill_gradient(low = "white", high = "grey") +
    labs(title = "Joint Probability Mass Function (PMF)", x = "X", y = "Y")

plot(ecdf(p_xy), main="Joint Cumulative Distribution Function (CDF)", 
     xlab="P(X, Y)", ylab="F(X, Y)", col="red")



```

Problem 3:
By generating 10,000 searches in R, carry out a simulation experiment for a 
search engine going through a list of sites for a given key phrase, until the 
key phrase is found. You should allow your program to input the probability 
p that any site will contain the key phrase.

Plot the simulated pdf and calculate its mean and variance, and obtain the 
simulated conditional distribution of searches when three searches have been 
carried out without success. Calculate its mean and variance, and satisfy 
yourself that they are equivalent to the simulated distribution of the 
complete set. As test data assume each site has a 60% chance of containing the 
key phrase. To satisfy yourself that the Markov memoryless property holds, 
obtain estimates of

(a) P(X = 4 given X > 3) and P(X = 1) 
(b) P(X = 5 given X > 3) and P(X = 2)

where X is the number of searches to the first success.
```{r}
repeat {
    cat("p is the probability that any site will contain the key phrase 
        (must be between 0 and 1): ")
    
    p <- as.numeric(readline("Enter value of p: "))

    if (!is.na(p) && p > 0 && p < 1) {
        cat(sprintf("Probability that any site will contain the key phrase is 
                    %f.\n", p))
        break
    }

    cat("\nInvalid input. Enter a value between zero and one.\n")
}

num_simulations <- 10000
searches <- rgeom(num_simulations, prob = p) + 1


hist(searches, xlab = "Number of Searches", main = "Simulated PDF", col = "pink")

mean_searches <- mean(searches)
var_searches <- var(searches)

cat(sprintf("\nMean number of searches: %f\n", mean_searches))
cat(sprintf("Variance of number of searches: %f\n", var_searches))

searches_given_3_failures <- searches[searches > 3]  
mean_given_3_failures <- mean(searches_given_3_failures)
var_given_3_failures <- var(searches_given_3_failures)

cat(sprintf("\nMean number of searches given at least 3 failures: %f\n",
            mean_given_3_failures))
cat(sprintf("Variance of number of searches given at least 3 failures: %f\n", 
            var_given_3_failures))

prob_X4_given_X3 <- sum(searches == 4) / sum(searches >= 3)
prob_X1 <- sum(searches == 1) / num_simulations
prob_X5_given_X3 <- sum(searches == 5) / sum(searches >= 3)
prob_X2 <- sum(searches == 2) / num_simulations

cat("\nMemoryless property estimates:\n")
cat(sprintf("P(X = 4 | X > 3): %f\n", prob_X4_given_X3))
cat(sprintf("P(X = 1): %f\n", prob_X1))
cat(sprintf("P(X = 5 | X > 3): %f\n", prob_X5_given_X3))
cat(sprintf("P(X = 2): %f\n", prob_X2))

```
