---
title: "FA E1"
output:
  pdf_document: default
  html_document: default
date: "2025-02-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

13. A malicious spyware can infect a computer system though the Internet or
through email. The spyware comes through the Internet 70% of the time
and 30% of the time, it gets in through email. If it enters via the Internet
the anti-virus detector will detect it with probability 0.6, and via email, it is
detected with probability 0.8.
(a) What is the probability that this spyware infects the system?
(b) If the spyware is detected, what is the probability that it came through the
Internet?

```{r}
spyware_through_internet <- 0.7
spyware_through_email <- 0.3
detector_internet <- 0.6
detector_email <- 0.8
detected_internet <- spyware_through_internet * detector_internet
detected_email <- spyware_through_email * detector_email
total_detected <- detected_internet + detected_email
infect_internet <- spyware_through_internet * (1 - detector_internet)
infect_email <- spyware_through_email * (1 - detector_email)
total_infected <- infect_internet + infect_email


spyware <- c("internet", "email")
probability_of_getting_through <- c(spyware_through_internet, spyware_through_email)
probability_of_getting_detected <- c(detector_internet, detector_email)
spyware_detected <- c(detected_internet, detected_email)
probability_of_getting_infected <- c(infect_internet, infect_email)

df <- data.frame(spyware, probability_of_getting_through, probability_of_getting_detected, 
                 spyware_detected, probability_of_getting_infected)
final.df <- rbind(df, c("Total", NA, NA, total_detected, total_infected))
final.df

cat(sprintf("The probability that the spyware infects the system is %.1f%%\n"
            , total_infected * 100))
cat(sprintf("If the spyware is detected, the probablity it came from the internet
            is %.1f%%\n", (detected_internet/total_detected) * 100))
```


14. Of the emails you receive 20% are spam on average. Your spam filter is able to
detect 90% of them but also misclassifies as spam 15% of the genuine emails.
(a) If an email arrives and is marked spam, what is the probability that it really
is spam?
(b) If an email arrives and is not marked spam, what is the probability that it
is legitimate?

```{r}
spam_email <- 0.2
genuine_email <- 1 - spam_email
spam_filter_detect <- 0.9
spam_filter_misclassified <- 0.15
spam_marked_as_spam <- spam_email * spam_filter_detect
spam_marked_as_genuine <- spam_email - spam_marked_as_spam
genuine_marked_as_spam <- genuine_email * spam_filter_misclassified
genuine_marked_as_genuine <- genuine_email - genuine_marked_as_spam
total_marked_as_spam <- spam_marked_as_spam + genuine_marked_as_spam
total_marked_as_genuine <- spam_marked_as_genuine + genuine_marked_as_genuine

emails <- c("spam", "genuine")
percent_of_emails <- c(spam_email, genuine_email)
probability_of_marked_as_spam <- c(spam_filter_detect, spam_filter_misclassified)
marked_as_spam <- c(spam_marked_as_spam, genuine_marked_as_spam)
marked_as_genuine <- c(spam_marked_as_genuine, genuine_marked_as_genuine)

df <- data.frame(emails, percent_of_emails, probability_of_marked_as_spam, 
                 marked_as_spam, marked_as_genuine)
final.df <- rbind(df, c("Total", NA, NA, total_marked_as_spam, 
                        total_marked_as_genuine))
final.df

cat(sprintf("If an email arrives and is marked spam, the probability that it is 
            really spam is %.2f%%\n", (spam_marked_as_spam/total_marked_as_spam)
            * 100))
cat(sprintf("If an email arrives and is not marked spam, the probablity that it 
            is legitimate is %.2f%%\n", (genuine_marked_as_genuine/total_marked_as_genuine)
            * 100))

```

