---
title: "SEC1-FA 2 GROUP 10-CESISTA, KJ;DELA ROSA, R-FA2"
output: pdf_document
date: "2025-02-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Use R to illustrate that the probability of getting:
(a) a head is 0.5 if a fair coin is tossed repeatedly;

```{r}
n <- 1000 # Number of trials
# Coin Toss Simulation
coin_toss <- sample(c("Head", "Tail"), n, replace = TRUE)
result_heads <- cumsum(coin_toss == "Head") / (1:n)
mean(coin_toss == "Head")

```

(b) a red card is 0.5 if cards are drawn repeatedly with replacement from awell-shuffled deck;

```{r}
# Red Card Draw Simulation
red_card <- sample(c("Red", "Black"), n, replace = TRUE)
result_red <- cumsum(red_card == "Red") / (1:n)
mean(red_card == "Red")

```

(c) an even number is 0.5 if a fair die is rolled repeatedly.

```{r}
# Die Roll Simulation
dice_roll <- sample(1:6, n, replace = TRUE)
result_even <- cumsum(dice_roll %% 2 == 0) / (1:n)
mean(dice_roll %% 2 == 0)
```

## Plots

```{r}
par(mfrow = c(1, 3)) # 3 plots in one row
plot(1:n, result_heads, type = "l", col = "blue", lwd = 2, ylim = c(0, 1),
main = "Coin Toss: P(Head)", xlab = "Number of Tosses", ylab = "Probability")
1
abline(h = 0.5, col = "red", lty = 2)
plot(1:n, result_red, type = "l", col = "blue", lwd = 2, ylim = c(0, 1),
main = "Red Card Draw: P(Red)", xlab = "Number of Draws", ylab = "Probability")
abline(h = 0.5, col = "red", lty = 2)
plot(1:n, result_even, type = "l", col = "blue", lwd = 2, ylim = c(0, 1),
main = "Die Roll: P(Even)", xlab = "Number of Rolls", ylab = "Probability")
abline(h = 0.5, col = "red", lty = 2)

par(mfrow = c(1, 1)) # Reset layout
```

## Results (n = 20)

```{r}
head(data.frame(Coin_Toss = coin_toss, Red_Card = red_card, Die_Roll = dice_roll), 20)
```

4. Amy and Jane are gambling together. A fair coin is tossed repeatedly. Each time a head comes up, Amy wins two euro from Jane, and each time a tail comes up, Amy loses two euro to Jane. Use R to simulate this game 100 times, and estimate:

(a) the number of times that Amy is ahead in these 100 tosses;

(b) how much Amy has won or lost after 100 tosses.

```{r}
gambling <- function (tosses, amy_wins, amy_money, amy_ahead){
  outcome <- c()
  results <- data.frame(
        outcome = character(0),
        amys_wins = integer(0),
        amys_ahead = integer(0),
        amys_money = numeric(0)
    )
    for (i in 1:tosses){
        coin_flip <- sample(c("H", "T"), size = 1, replace = TRUE)
        outcome <- c(outcome, coin_flip)

        if (coin_flip == "H") {
            amy_wins <- amy_wins + 1 #adds a win to Amy
            amy_money <- amy_money + 2 #adds two euros to Amy's total
        } else {
            amy_money <- amy_money - 2 #takes two euros from Amy's total
        }

        if (amy_money > 0) { #Amy is ahead of Jane in terms of wins if her balance is positive
            amy_ahead <- amy_ahead + 1
        }

        results <- rbind(results, data.frame(
            outcome = coin_flip,
            amys_wins = amy_wins,
            amys_ahead = amy_ahead,
            amys_money = amy_money
        ))
        
    }
  
    print("(a) the number of times that Amy is ahead in these 100 tosses;")
    print(sprintf("Amy won a total of %d times", amy_wins))
    print(sprintf("Amy was ahead of Jane a total of %d times during the game", amy_ahead)) # answer to (a)
    
    print("(b) how much Amy has won or lost after 100 tosses.")
    if (amy_money > -1) {
      print(sprintf("Amy won a total of %d euros", amy_money)) #answer to (b) 
    } else {
      print(sprintf("Amy lost a total of %d euros", abs(amy_money))) #answer to (b) 
    }


    head(results, 10) #first ten ouctomes of the coin flip
}

gambling(100, 0, 0, 0)
```

