---
title: "SEC1-FA3-GROUP-10-CESISTA,-KJ-FA3"
output: pdf_document
date: "2025-02-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

2.  A binary communication channel carries data as one of two sets of signals denoted by 0 and 1. Owing to noise, a transmitted 0 is sometimes received as a 1, and a transmitted 1 is sometimes received as a 0. For a given channel, it can be assumed that a transmitted 0 is correctly received with probability 0.95, and a transmitted 1 is correctly received with probability 0.75. Also, 70% of all messages are transmitted as a 0. If a signal is sent, determine the probability that:

(a) a 1 was received;
(b) a 1 was transmitted given than a 1 was received.

```{r}
signal_transmitted_0 <- 0.7
signal_transmitted_1 <- 1 - signal_transmitted_0
received_correctly_0 <- 0.95
received_correctly_1 <- 0.75
transmitted_0_received_0 <- signal_transmitted_0 * received_correctly_0
transmitted_0_received_1 <- signal_transmitted_0 * (1-received_correctly_0)
transmitted_1_received_0 <- signal_transmitted_1 * (1-received_correctly_1)
transmitted_1_received_1 <- signal_transmitted_1 * received_correctly_1
total_received_as_0 <- transmitted_0_received_0 + transmitted_1_received_0
total_received_as_1 <- transmitted_0_received_1 + transmitted_1_received_1

signals <- c(0, 1)
percent_of_all_messages <- c(signal_transmitted_0, signal_transmitted_1)
received_correctly <- c(received_correctly_0, received_correctly_1)
received_as_0 <- c(transmitted_0_received_0, transmitted_1_received_0)
received_as_1 <- c(transmitted_0_received_1, transmitted_1_received_1)

df <- data.frame(signals, percent_of_all_messages, received_correctly, received_as_0, received_as_1)
final.df <- rbind(df, c("Total", NA, NA, total_received_as_0, total_received_as_1))
final.df

cat(sprintf("The probability that a 1 was received is %.1f%%.\n", total_received_as_1 * 100))
cat(sprintf("The probability that a 1 was transmitted given that a 1 was received is %.1f%%.\n", 
            transmitted_1_received_1 * 100))
```

7.  There are three employees working at an IT company: Jane, Amy, and Ava, doing 10%, 30%, and 60% of the programming, respectively. 8% of Jane’s work, 5% of Amy’s work, and just 1% of Ava‘s work is in error. What is the overall percentage of error? If a program is found with an error, who is the most likely person to have written it?

```{r}
jane_work <- 0.1
amy_work <- 0.3
ava_work <- 0.6

jane_error <- 0.08
amy_error <- 0.05
ava_error <- 0.01

jane_error_done <- jane_error * jane_work
amy_error_done <- amy_error * amy_work
ava_error_done <- ava_error * ava_work

Name <- c("Jane", "Amy", "Ava")
Percentage_of_Work <- c(jane_work, amy_work, ava_work)
Percentage_of_Error <- c(jane_error, amy_error, ava_error)
Percentage_of_Error_Done <- c(jane_error_done, amy_error_done, ava_error_done)
Overall_Percentage_of_Error <- sum(c(jane_error_done, amy_error_done, ava_error_done))

df <- data.frame(Name, Percentage_of_Work, Percentage_of_Error, Percentage_of_Error_Done)
final.df <- rbind(df, c("Overall", NA, NA, Overall_Percentage_of_Error))
final.df

highest_error <- max(df$Percentage_of_Error_Done)
person_with_highest_error <- df[df$Percentage_of_Error_Done == highest_error, "Name"]

cat(sprintf("The overall percentage of error is %.1f%%.\n", Overall_Percentage_of_Error * 100))
cat(sprintf("TIf a program is found with an error, the person most likely to have written it is %s.\n", 
            person_with_highest_error))
```
